Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-05-23 paper.tex
Spelling pass

Censorship circumvention has developped over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.

@@

Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol/service, or using an existing protocol/service as intended. Of these, mimicry was eliminated as a functional technique. Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimiced in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol. The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever suceed due to the daunting list of reqirements that an imitator must satisfy. The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}

Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended. We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques. High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels. These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g. if a circumvention system uses email effectively, it may only be possible to block by blocking email. We discuss several examples of both low and high bandwidth channels in the following sections.

Lower and higher bandwidth transports can be combined to work together and gain benefits of both. Most higher-bandwidth channels require conveying some less-fixed \emph{out-of-band} information (e.g. an IP address) to use a higher bandwidth channel. Low bandwidth channels, generally being more costly to block, still require out-of-band information, but frequently this information is valid as long as the channel is functional. For example, an email-based channel will require a recipient email address, but this email address could be effectively constant due to the way email itself functions. As a result, an email based channel may effectively hard-code this information in the transport itself, allowing the channel to be used as long as you have the code and an adversary that does not block email. This highly resiliant but low-bandwidth setup may be used to bootstrap higher bandwidth channels. An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the recieved point-to-point channel is blocked. With this synergy between the low and high bandwidth channels, discussing and understanding both is crucial to a modern circumvention system.

@@

As censorship apparati developped, DPI began being used. DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets. [TODO: xref DPI] OBFS2 was developped by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI. Obfs2 was vulnerable however, as a passive MITM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using. Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response. They may potentially continue probing depending on the response. [TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}

obfs3 was developped to patch issues with obfs2. The main issue it addressed was the ability to perform passive decryption of the flow. This was done by using a custom Diffie-Hellman handshake.\cite{obfs3} obfs3 was still vulnerable to active probing.\cite{scramblesuit} Scramblesuit was designed to address this flaw, as well as several other identified tells of obfs3.\cite{scramblesuit} Scramblesuit defined a strong adversary, similar to the one proposed in this paper, and aimed to tackle active probing while also introducing basic traffic shaping via padding as well as inter-arrival times - introducing the concept of a polymorphic traffic shape for a protocol.\footnote{Polymorphic shaping is a promising defense for circumventors. The basic concept is that if every server has a unique traffic shape, then even if an adversary is able to identify a single server effectively, they will be unable to use that information in blocking other servers. This concept has not been fully exploited by a published circumvention technique at the time of writing.} Scramblesuit introduced the addition of a shared secret distributed \emph{out-of-band} to enable these improvements. From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform diffie-hellman key exchange, and then a data exchange phases.

>>>>

Censorship circumvention has developed over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.

@@

Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicking an existing protocol/service, or using an existing protocol/service as intended. Of these, mimicry was eliminated as a functional technique. Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimicked in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol. The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever succeed due to the daunting list of requirements that an imitator must satisfy. The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}

Beyond mimicry, most systems fall into either looking like an unknown protocol, or using an existing protocol as intended. We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques. High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other trade-offs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels. These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g. if a circumvention system uses email effectively, it may only be possible to block by blocking email. We discuss several examples of both low and high bandwidth channels in the following sections.

Lower and higher bandwidth transports can be combined to work together and gain benefits of both. Most higher-bandwidth channels require conveying some less-fixed \emph{out-of-band} information (e.g. an IP address) to use a higher bandwidth channel. Low bandwidth channels, generally being more costly to block, still require out-of-band information, but frequently this information is valid as long as the channel is functional. For example, an email-based channel will require a recipient email address, but this email address could be effectively constant due to the way email itself functions. As a result, an email based channel may effectively hard-code this information in the transport itself, allowing the channel to be used as long as you have the code and an adversary that does not block email. This highly resilient but low-bandwidth setup may be used to bootstrap higher bandwidth channels. An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the received point-to-point channel is blocked. With this synergy between the low and high bandwidth channels, discussing and understanding both is crucial to a modern circumvention system.

@@

As various censorship apparatuses developed, DPI began being used. DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets. [TODO: xref DPI] OBFS2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI. Obfs2 was vulnerable however, as a passive MitM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using. Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response. They may potentially continue probing depending on the response. [TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}

obfs3 was developed to patch issues with obfs2. The main issue it addressed was the ability to perform passive decryption of the flow. This was done by using a custom Diffie-Hellman handshake.\cite{obfs3} obfs3 was still vulnerable to active probing.\cite{scramblesuit} Scramblesuit was designed to address this flaw, as well as several other identified tells of obfs3.\cite{scramblesuit} Scramblesuit defined a strong adversary, similar to the one proposed in this paper, and aimed to tackle active probing while also introducing basic traffic shaping via padding as well as inter-arrival times - introducing the concept of a polymorphic traffic shape for a protocol.\footnote{Polymorphic shaping is a promising defense for circumventors. The basic concept is that if every server has a unique traffic shape, then even if an adversary is able to identify a single server effectively, they will be unable to use that information in blocking other servers. This concept has not been fully exploited by a published circumvention technique at the time of writing.} Scramblesuit introduced the addition of a shared secret distributed \emph{out-of-band} to enable these improvements. From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform Diffie-Hellman key exchange, and then a data exchange phases.
